% List of abbreviations
\begin{mclistof}{List of Abbreviations}{3.2cm}
    \item[AR-BTS] Boltzmann Tree Search with Average Returns.
    \item[AR-DENTS] Decaying ENtropy Tree Search with Average Returns.
    \item[AR-MENTS] Maximum ENtropy Tree Search with Average Returns.
    \item[AR-RENTS] Relative ENtropy Tree Search with Average Returns.
    \item[AR-TENTS] Tsallis ENtropy Tree Search with Average Returns.
    \item[BTG] Bipartite Triangulation Graph.
    \item[BTS] Boltzmann Tree Search.
    \item[C-CHMCTS] Chebyshev Convex Hull Monte Carlo Tree Search.
    \item[CCS] Convex Coverage Set.
    \item[CH-BTS] Convex Hull Boltzmann Tree Search.
    \item[CH-CZT] Convex Hull Contextual Zooming for Trees.
    \item[CHMCTS] Convex Hull Monte Carlo Tree Search.
    \item[CH-UCT] Convex Hull UCT.
    \item[CHVI] Convex Hull Value Iteration.
    \item[CHVS] Convex Hull Value Set.
    \item[CMAB] Contextual Multi-Armed Bandit (problem).
    \item[CZ] Contextual Zooming. 
    \item[CZT] Contextual Zooming for Trees.
    \item[DENTS] Decaying ENtropy Tree Search.
    \item[DGW] DeterministicGridWorld (environment).
    \item[DKW] Dvoretzky-Kiefer-Wolfowitz (inequality).
    \item[DST] Deep Sea Treasure (environment). 
    \item[EMAB] Exploring Multi-Armed Bandit (problem).    
    \item[EUM] Expected Utility Metric.
    \item[GT] Good-Turing (estimate).
    \item[H-CHMCTS] Hypervolume Convex Hull Monte Carlo Tree Search.
    \item[H-MCTS] Hybrid MCTS.
    \item[HOO] Hierarchical Optimistic Optimisation.
    \item[HV] Hypervolume (indicator).
    \item[LEB] Longest Edge Bisection.
    \item[MAB] Multi-Armed Bandit (problem). 
    \item[MaxUCT] Maximum UCT.
    \item[MCCS] Minimal Convex Coverage Set.
    \item[MCTS] Monte Carlo Tree Search.
    \item[\mctsone] A specific and common presentation of Monte Carlo Tree Search, presented in Section \ref{sec:2-4-thts}.
    \item[MDP] Markov Decision Process.
    \item[MENTS] Maximum ENtropy Tree Search.
    \item[MOMCTS] Multi-Objective Monte Carlo Tree Search.
    \item[MOMDP] Multi-Objective Markov Decision Process.
    \item[MORL] Multi-Objective Reinforcement Learning.
    \item[P-CHMCTS] Pareto Convex Hull Monte Carlo Tree Search.
    \item[PF] Pareto Front.
    \item[PUCT] Predictor-UCT. 
    \item[RENTS] Relative ENtropy Tree Search.
    \item[RL] Reinforcement Learning.
    \item[SM-BTS] Boltzmann Tree Search with Simplex Maps.
    \item[SM-DENTS] Decaying ENtropy Tree Search with Simplex Maps.
    \item[TENTS] Tsallis ENtropy Tree Search.
    \item[THTS] Trial-Based Heuristic Tree Search.
    \item[\thtspp] An extension of THTS used in this thesis.
    \item[UCB] Upper Confidence Bound (algorithm).
    \item[UCT] Upper Confidence Bound Applied to Trees.
\end{mclistof} 


% List of notation
\begin{mclistof}{List of Notation}{3.2cm}
    %%%%%
    % General Maths
    %%%%%
    \item[\Large\textbf{General Notation}\hfill\hfill]
    \item[$\one$] 
        The indicator function, where $\one(A)=1$ when $A$ is true, and $\one(A)=0$ when $A$ is false. 
    \item[$\hat{A}$] 
        The hat notation is used to denote an estimate, i.e. $\hat{A}$ is an estimate for some value $A$ or some optimal value $A^*$
    \item[$\bar{A}$] 
        The bar notation is used to denote sample averages, $\bar{A}$ is a sample average of a number of samples $A_1,...,A_k$. i.e. $\bar{A}=\frac{1}{k}\sum_{i=1}^k A_i$.
    \item[$\tilde{A}$] 
        The tilde notation is used to denote a (function) approximation, such as a neural network.
    \item[$\cl{A}$] 
        Calligraphic font is used to denote variables that are sets or tuples (ordered sets).
    \item[$\bff{A}$] 
        Bold font is used to denote vectors, and $A_i$ is used to denote the $i$th component of the vector $\bff{A}$.
    \item[$\texttt{A}$]
        Typewriter text is used to refer to variables relating to an algorithm (or the analysis of an algorithm).
    \item[$\bfcl{A}$] 
        The notations above will also be combined at times, so $\bfcl{A}$ is used to denote a set that contains vectors.
    \item[$\bb{E}$] 
        The expectation operator. $\bb{E}[f]$ denotes the expectation of a distribution $f$, and $\bb{E}_{x\sim f}[g(x)]$ denotes the expected value of $g(x)$ under the distribution $f$.
    \item[$x\sim f$] 
        If $f:X\rightarrow\bb{R}$ specifies a probability distribution in some way (e.g. a probability density function or cumulative density function), then $x\sim f$ denotes that the variable $x$ is sampled from the distribution $f$.
    \item[$O(f(x))$]
        Big-O notation: $g(x) = O(f(x))$ if there exist constants $c > 0$ and $x_0$ such that $|g(x)| \leq c \cdot f(x)$ for all $x \geq x_0$. Used to describe an asymptotic upper bound on the growth rate of a function. If $f$ is a set, then $x\sim f$ denotes that the variable $x$ is sampled uniformly randomly from the set $f$.
    \item[$X_i\rap X$]
        The sequence of random variables $X_i$ converges in probability to the random variable $X$. $\Pr\left(\left|X_i - X\right| > \varepsilon\right) \rightarrow 0 \ \text{as} \ i \rightarrow \infty$ for all $\varepsilon>0$.
    \item[$X_i\raas X$]
        The sequence of random variables $X_i$ converges almost surely to the random variable $X$. $\Pr\left(\lim_{i\rightarrow\infty} X_i = X\right) = 1$.
    % \\
    % %%%%%
    % % MABs - notation is local to background section + 
    % %%%%%
    % \item[\Large\textbf{Multi-Armed Bandits (Section \ref{sec:2-3-mab})}\hfill\hfill]
    % \item[$x$] \todo{define here and move into correct place in the list}
    % \item[$y$] \todo{define here and move into correct place in the list}
    % \item[$f_i$] \todo{define here and move into correct place in the list}
    % \item[$x^m$] \todo{define here and move into correct place in the list}
    % \item[$y^m$] \todo{define here and move into correct place in the list}
    % \item[$\bar{y}_i^m$] \todo{define here and move into correct place in the list}
    % \item[$N$] \todo{define here and move into correct place in the list}
    % \item[$\mu_i$] \todo{define here and move into correct place in the list}
    % \item[$\mu^*$] \todo{define here and move into correct place in the list}
    % \item[$\creg_{\mab}$] \todo{define here and move into correct place in the list}
    % \item[$\pi(m)$] \todo{define here and move into correct place in the list. Maybe keep it as this and ask question}
    % \item[$m$] \todo{define here and move into correct place in the list}
    % \item[$\pi_{\ucb}(m)$] \todo{define here and move into correct place in the list}
    % \item[$\pi^m$] \todo{define here and move into correct place in the list}
    % \item[$\psi^m$] \todo{define here and move into correct place in the list}
    % \item[$w$] \todo{define here and move into correct place in the list}
    % \item[$w^m$] \todo{define here and move into correct place in the list}
    % \item[$\mu_{w,i}$] \todo{define here and move into correct place in the list}
    % \item[$\mu_{w}^*$] \todo{define here and move into correct place in the list}
    % \item[$W$] \todo{define here and move into correct place in the list}
    % \item[$ $] \todo{define here and move into correct place in the list}
    % \item[$ $] \todo{define here and move into correct place in the list}
    % \item[$ $] \todo{define here and move into correct place in the list}
    % \item[$ $] \todo{define here and move into correct place in the list}
    \\
    %%%%%
    % (MO)MDPs
    %%%%%
    \item[{\parbox[t]{\textwidth}{
            \Large\textbf{(Multi-Objective) Markov Decision Processes \\(Defined in Sections \ref{sec:2-2-mdps} and \ref{sec:2-6-morl})}\hfill\hfill
          }}]
    \item[$\cl{A}$]
        A (finite) set of actions.
    \item[$a_t$]
        The action at the $t$th timestep of a trajectory.
    \item[$D$]
        The dimension of rewards in a MOMDP.
    \item[$H$]
        The finite-horizon time bound of an MDP.
    \item[$\cl{M}$]
        A Markov Decision Process, which is a tuple $\cl{M}=(\cl{S},s_0,\cl{A},R,p,H)$.
    \item[$\bfcl{M}$] 
        A Multi-Objective Markov Decision Process, which is a tuple $\bfcl{M}=(\cl{S},s_0,\cl{A},\bff{R},p,H)$.
    \item[$p$] 
        The next-state transition distribution of an MDP. $p(s' | s,a)$ is the probability of transitioning to state $s'$ from state $s$ by taking action $a$.
    \item[$\pi$]
        A policy, mapping a state $s\in\cl{S}$ to a probability distribution over actions $\cl{A}$. That is, $\pi(a|s)$ is the probability of taking action $a$ at state $s$. $\pi(s)=a'$ is used a shorthand for $\pi(a|s)=\one[a=a']$.
        % \todo{probably dont need this, not going to use non-locally}
    \item[$R$] 
        The reward function of an MDP: $R(s,a)$ is the reward received from taking action $a$ at state $s$.
    \item[$\bff{R}$] 
        The $D$ dimensional reward function of a MOMDP: $\bff{R}(s,a)\in\bb{R}^D$ is the vector of rewards received from taking action $a$ at state $s$.
    \item[$r_t$]
        The reward at the $t$th timestep of a trajectory.
    \item[$\cl{S}$]
        A (finite) set of states.
    \item[$\cl{S}_0$]
        The set of reachable states from the starting state $s_0$ in an MDP.
    \item[$\suc{s}{a}$]
        The set of successor states of a state-action pair $(s,a)$, with respect to an MDP: $\suc{s}{a}=\{s'\in\cl{S}|p(s'|s,a)>0\}$.
    \item[$s_0$]
        $s_0\in\cl{S}$ is the initial starting state of an MDP.
    \item[$s_t$]
        The state at the $t$th timestep of a trajectory.
    \item[$\terminal$]
        $\terminal\subseteq\cl{S}$ is the set of terminal states. A state is terminal if the transition distribution and reward function of the MDP are such that once reached, the state will never be left and no more reward will be received.
    \item[$\tau$]
        A trajectory, or sequence, of states, actions and rewards that are sampled according to a policy $\pi$ and an MDP $\cl{M}$: $\tau = (s_0, a_0, r_0, s_1, ..., s_{H-1}, a_{H-1}, r_{H-1}, s_H)$.
    \item[$\bff{\tau}$]
        A multi-objective trajectory, of states, actions and rewards that are sampled according to a policy $\pi$ and an MDP $\cl{M}$: $\bff{\tau} = (s_0, a_0, \bff{r}_0, s_1, ..., s_{H-1}, a_{H-1}, \bff{r}_{H-1}, s_H)$.
    % \item[$s,(s,a)\in\tau$] 
    %     \todo{define this here?} 
    \item[$\tau_{i:j}$]
        A truncated trajectory, starting at timestep $i$, and ending at timestep $j$: $\tau_{i:j} = (s_i, a_i, r_i, s_{i+1}, ..., s_{j-1}, a_{j-1}, r_{j-1}, s_j)$. 
    \item[$\bff{\tau}_{i:j}$] 
        A multi-objective truncated trajectory, starting at timestep $i$ and ending at timestep $j$: $\bff{\tau}_{i:j} = (s_i, a_i, \bff{r}_i, s_{i+1}, ..., s_{j-1}, a_{j-1}, \bff{r}_{j-1}, s_j)$.
    \\
    %%%%%
    % RL
    %%%%%
    \item[{\parbox[t]{\textwidth}{
            \Large\textbf{Reinforcement Learning (Section \ref{sec:2-3-rl})}\hfill\hfill
          }}]
    \item[$J(\pi)$] 
        The objective function for (standard) reinforcement learning: $J(\pi) = V^{\pi}(s_0;0)$.
    \item[$\pi^*$]
        The optimal standard policy, that maximises the objective function $J(\pi)$.
    \item[$Q^*$]
        The optimal Q-value function. $Q^*(s,a;t)$ denotes the maximal expected value that can be achieved by any policy, starting from state $s_t=s$, with action $a_t=a$.
    % \item[$\hat{Q}^k$]
    %     The estimate of the optimal value function after $k$ iterations of Value Iteration. 
    %     \todo{probably dont need this, not going to use non-locally}
    \item[$Q^{\pi}$]
        The Q-value function of a policy $\pi$. $Q^{\pi}(s,a;t)$ denotes the expected cumulative reward that policy $\pi$ will obtain, starting from state $s_t=s$, starting by taking action $a_t=a$.
    \item[$V^*$]
        The optimal value function. $V^*(s;t)$ denotes the maximal expected value that can be achieved by any policy, starting from state $s_t=s$.
    % \item[$\hat{V}^k$]
    %     The estimate of the optimal value function after $k$ iterations of Value Iteration.
    %     \todo{probably dont need this, not going to use non-locally}
    \item[$V^{\pi}$]
        The value of a policy $\pi$. $V^{\pi}(s;t)$ denotes the expected cumulative reward that policy $\pi$ will obtain, starting from state $s_t=s$.
    \\
    %%%%%
    % MERL
    %%%%%
    \item[{\parbox[t]{\textwidth}{
        \Large\textbf{Maximum Entropy Reinforcement Learning \\(Section \ref{sec:2-3-1-merl})}\hfill\hfill
      }}]
    \item[$\alpha$] 
        The temperature parameter, or, the coefficient of the entropy term in the maximum entropy (soft) objective.
    \item[$\cl{H}$]
        The Shannon entropy, of a probability distribution or policy.
    \item[$J_{\sft}(\pi)$] 
        The objective function for maximum entropy (soft) reinforcement learning: $J_{\sft}(\pi) = V_{\sft}^{\pi}(s_0;0)$.
    \item[$\pi_{\sft}^*$]
        The optimal soft policy, that maximises the soft objective function $J_{\sft}(\pi)$.
    \item[$Q_{\sft}^*$]
        The optimal soft Q-value function. $Q_{\sft}^*(s,a;t)$ denotes the maximal expected soft value that can be achieved by any policy, from state $s_t=s$ and taking action $a_t=a$. 
    \item[$Q_{\sft}^{\pi}$]
        The soft Q-value function of a policy $\pi$. $Q_{\sft}^{\pi}(s,a;t)$ is the expected value of the policy from $s_t=s$, starting with action $a_t=a$, with an addition of the entropy of the policy weighted by the temperature $\alpha$.
    \item[$V_{\sft}^*$]
        The optimal soft value function. $V_{\sft}^*(s;t)$ denotes the maximal expected soft value that can be achieved by any policy, from state $s_t=s$. 
    \item[$V_{\sft}^{\pi}$]
        The soft value of a policy $\pi$. $V_{\sft}^{\pi}(s;t)$ is the expected value of the policy from $s_t=s$, with an addition of the entropy of the policy weighted by the temperature $\alpha$.
        \\
    %%%%%
    % THTS
    %%%%%
    \item[{\parbox[t]{\textwidth}{
        \Large\textbf{Trial Based Heuristic Tree Search (Section \ref{sec:2-4-thts})}\hfill\hfill
        }}]
    \item[$\backupv$]
        Updates the values at a decision node in the backup phase of a trial \thtspp, using the decision node's children, the trajectory sampled for the trial and the heuristic value function.
    \item[$\backupq$] 
        Updates the values at a chance node in the backup phase of a trial \thtspp, using the chance node's children, the trajectory sampled for the trial and the heuristic value function.
    \item[$H_{\thtspp}$]
        The planning horizon used in \thtspp, with $H_{\thtspp}\leq H$.
    \item[$N(s)$]
        The number of visits at the decision node corresponding to state $s$.
    \item[$N(s,a)$]
        The number of visits at the chance node corresponding to state-action pair $(s,a)$.
    \item[$N(s'|s,a)$]
        The \textnormal{conditional visit count} at chance node $(s,a)$, which is the number of times successor state $s'$ was sampled from $(s,a)$ across all \thtspp\ewe trials.
    \item[$\node(s)$] 
        The decision node corresponding to the state $s$.
    \item[$\node(s)\dotchildren$]
        The set of chance nodes that are children of $\node(s)$.
    \item[$\dnodedata{s}$]
        The set of variables stored at decision node $\node(s)$, typically used for estimating values.
    \item[$\node(s,a)$] 
        The chance node corresponding to the state-action pair $(s,a)$.
    \item[$\node(s,a)\dotchildren$]
        \hspace{0.25cm} The set of decision nodes that are children of $\node(s,a)$.
    \item[$\cnodedata{s,a}$] 
        The set of variables stored at chance node $\node(s,a)$, typically used for estimating Q-values.
    \item[$\piinit$]
        A heuristic policy, which can be used by the search policy to utilise prior knowledge of the environment.
    \item[$\pisearch$]
        The search policy used in \thtspp\ewe to sample a trajectory in the selection phase.
    \item[$\Qinit$]
        The heuristic action function used in \thtspp, used to provide a Q-value estimate for any state-action pairs that aren't in the search tree.
    \item[$\samplecontext$]
        A function used in \thtspp\ewe that creates a context, or key-value store, and samples any initial values to be stored in the context.
    \item[$\sampleoutcome$]
        A function used in \thtspp\ewe to sample outcomes (successor states) from the environment (MDP).
    \item[$\selectaction$]
        A function used in \thtspp\ewe to select an action at a decision node.
    \item[\mctsmode] %single_node_expansion
        \hspace{1.35cm} Specifies if \thtspp\ewe samples a trajectory such that only one decision node is added to the search tree per trial. If not running with \mctsmode\ewe set, \thtspp\ewe samples a trajectory until a terminal state or the planning horizon $H_{\thtspp}$ is reached.
    \item[$\cl{T}$] 
        The \thtspp\ewe search tree. $\cl{T}\subseteq \cl{S} \cup \cl{S}\times\cl{A}$. Initially it consists of the root node, and new nodes are added from the trajectories/trials sampled in the selection phase.
    \item[\graphmode] %transposition_table
        \hspace{1cm} Specifies if \thtspp\ewe uses a transposition table to store and re-use the decision nodes of the search tree when they are reached again via another path.
    \item[$\Vinit$]
        The heuristic value function used in \thtspp, used to initialise the value of a new decision node. 
    \\
    %%%%%
    % UCT
    %%%%%
    \item[{\parbox[t]{\textwidth}{
        \Large\textbf{Upper Confidence Bound applied to Trees (Section \ref{sec:2-4-2-uct})}\hfill\hfill
    }}]
    \item[$\buct$]
        The bias parameter used in UCT to control exploration.
    \item[$\normalisedq$]
        Specifies if the Q-values are linearly normalised (between 0 and 1) by the UCT search policy to select actions.
    \item[$\pirollout$] 
        A policy used to sample a trajectory that is used to estimate the value of a state being added to a search tree.
    \item[$\piuct$] 
        The search policy used in UCT.
    \item[$\Quct(s,a)$] 
        The sample-average value estimate used to estimate the Q-value at a chance node $(s,a)$ in UCT.
    \item[$\Quctnorm(s,a)$] 
        The optionally linearly normalised (between 0 and 1) Q-value. Used by the UCT search policy to select actions. If $\normalisedq$ is False, then $\Quctnorm(s,a)=\Quct(s,a)$. 
    \item[$\hat{V}^{\pirollout}(s)$] 
        An estimate of $V^{\pirollout}(s)$ computed using the return from a single trajectory sampled using policy $\pirollout$. It is used to initialise the value of a state being added to the search tree.
    \item[$\Vuct(s)$] 
        The sample-average value estimate used to estimate the value at a decision node $s$ in UCT. 
    \\
    %%%%%
    % MENTS
    %%%%%
    \item[{\parbox[t]{\textwidth}{
        \Large\textbf{Maximum ENtropy Tree Search (Section \ref{sec:2-4-4-ments})}\hfill\hfill
    }}]
    \item[$\alphaments$] 
        The temperature parameter used in MENTS, which is the coefficient of the entropy terms in the maximum entropy objective.
    \item[$\epsments$]
        An exploration parameter used in MENTS.
    \item[$\lambda(s,\epsilon)$] 
        A decaying function used to control and anneal exploration in MENTS. $\lambda(s,\epsilon) = \min\left(1,\frac{\epsilon}{\log(e+N(s))}\right)$.
    \item[$\tilde{\pi}$] 
        A policy neural network, used to initialise soft Q-value estimates in MENTS, if available. 
    \item[$\piments$] 
        The search policy used in MENTS.
    \item[$\Qments(s,a)$] 
        A soft Q-value estimate at the chance node $(s,a)$ in MENTS.
    \item[$\tilde{V}$] 
        A function approximation to $V^*$.
    \item[$\Vments(s)$] 
        A soft value estimate at the decision node $s$ in MENTS.
    \\
    % %%%%%
    % % Convergence
    % %%%%%
    % \item[{\parbox[t]{\textwidth}{
    %     \Large\textbf{Convergence of Random Variables (Section \ref{sec:2-5-convergence})}\hfill\hfill
    %     }}]
    % % \item[$F_m$] 
    % %     The empirical cumulative distribution function of $m$ samples drawn from the distribution with cumulative distribution function $F$: $F_m(x)=\frac{1}{m}\sum_{i=1}^m \one[X_i<x]$.
    % \item[$\missingmass$] 
    %     The \textnormal{missing mass} of a sample: the total probability assigned to categories that were not observed in the sample.
    % \item[$\goodturingestimate$]
    %     The \textnormal{Good-Turing estimate} of the missing mass: $\goodturingestimate = \frac{M_1}{m}$, where $M_1$ is the number of categories observed exactly once in a sample of size $m$.
    \\
    %%%%%
    % MORL
    %%%%%
    \item[{\parbox[t]{\textwidth}{
        \Large\textbf{Multi-Objective Reinforcement Learning \\(Section \ref{sec:2-6-morl})}\hfill\hfill
      }}]
    \item[$CCS(\Pi)$] 
        A convex coverage set of policies, which contains at least one policy that maximises the linear utility $u_{\lin}(\cdot;\bff{w})$ for each weight vector $\bff{w}$.
    \item[$MCCS(\Pi)$]
        The minimal convex coverage set of policies, which has no redundant policies and for each policy in $MCCS(\Pi)$ there is some weight that it uniquely (with respect to $MCCS(\Pi)$) obtains the optimal linear utility.
    \item[$CH(\Pi)$] 
        The undominated set of policies in $\Pi$ (the set of all possible policies), with respect to the linear utility function $u_{\lin}$. $CH(\Pi)=U(\Pi;u_{\lin})$.
    \item[$CS(\Pi;u)$] 
        A coverage set of policies, which contains at least one policy that maximises the utility $u(\cdot;\bff{w})$ for each weight vector $\bff{w}$.
    \item[$\cprune$] 
        An operation that takes an arbitrary set of vectors, and returns the subset that lie at the vertices of the geometric (partial) convex hull. 
    \item[$\Delta^D$] 
        The $D-1$ simplex simplex (with $D$ dimensions), or, the set of possible weightings over the $D$ objectives of a MOMDP. $\Delta^D = \{\bff{w}\in\bb{R}^D|w_i \geq 0, \sum_i w_i = 1\}$.
    \item[$\eum(\Psi)$]
        The \textnormal{expected utility metric} of a set of policies $\Psi$: $\eum(\Psi)=\bb{E}_{\bff{w}\sim U(\Delta^D)}[\max_{\psi\in\Psi}\bff{w}^\top\bff{V}^\psi(s_0)]$.
    \item[$\HV(\bfcl{V};\rref)$]
        The \textnormal{hypervolume indicator} of a vector set $\bfcl{V}$ with respect to a reference point $\rref$: the Lebesgue measure of the region dominated by $\bfcl{V}$ and bounded below by $\rref$.
    \item[$\Pi$] 
        The set of all possible policies in a MOMDP.
    \item[$PF(\Pi)$]
        The Pareto front of the set of policies $\Pi$.
    \item[$\bff{Q}^{\pi}$]
        The multi-objective Q-value function of a policy $\pi$. $\bff{Q}^{\pi}(s,a;t)$ denotes the expected cumulative vector reward that policy $\pi$ will obtain, starting from state $s_t=s$, starting by taking action $a_t=a$.
    \item[$\succ_P$]
        The \textnormal{Pareto domination} relation over vectors: $\bff{v}\succ_P\bff{v'}$ if and only if $v_i\geq v'_i$ for all $i$ and $v_j>v'_j$ for some $j$.
    \item[$U(\Pi;u)$] 
        The undominated set of policies in $\Pi$ (the set of all possible policies), with respect to the utility function $u$. Each policy in $U(\Pi;u)$ achieves a maximal utility for some weighting over the objectives.
    \item[$u$] 
        A utility function, mapping multi-objective values to scalar values, that depends on a weighting over objectives. The multi-objective value $\bff{V}^{\pi}(s;t)$ is mapped to $u(\bff{V}^{\pi}(s;t);\bff{w})$, where $\bff{w}$ is a weighting over the objectives.
    \item[$u_{\lin}$]
        The linear utility function: $u_{\lin}(\bff{v};\bff{w}) = \bff{w}^\top \bff{v}$.
    \item[$\bff{V}^{\pi}$]
        The multi-objective value of a policy $\pi$. $\bff{V}^{\pi}(s;t)$ denotes the expected cumulative reward that policy $\pi$ will obtain, starting from state $s_t=s$.
    \item[$\valset(\Pi')$] 
        The set of multi-objective values obtained by a set of policies $\Pi'$.
    \item[$\bff{w}$] 
        A weighting over objectives that quantifies preferences over the multiple objectives, to be used in a utility function.
    % \\
    % %%%%%
    % % CHVI
    % %%%%%
    % \item[{\parbox[t]{\textwidth}{
    %     \Large\textbf{Convex Hull Value Iteration \\(Section \ref{sec:2-6-1-chvi})}\hfill\hfill
    %   }}]
    % \item[Q value set]
    % \item[Scalar Q value]
    % \item[V value set]
    % \item[pi chvi]
    % \item[v bot, reference point] 
    \\
    %%%%%
    % Ch 4 - Boltzmann Search
    %%%%%
    \item[{\parbox[t]{\textwidth}{
        \Large\textbf{Monte Carlo Tree Search with Boltzmann Exploration \\(Chapter \ref{ch:4-dents})}\hfill\hfill
      }}]
    \item[$\sreg(s,\psi)$]
        The \textnormal{simple regret} of a recommendation policy $\psi$ at state $s$: $\sreg(s,\psi) = V^*(s) - V^{\psi}(s)$.
    \\
    %%%%%
    % BTS
    %%%%%
    \item[{\parbox[t]{\textwidth}{
        \Large\textbf{Boltzmann Tree Search (Section \ref{sec:4-2-1-bts})}\hfill\hfill
    }}]
    \item[$\alphabts$] 
        The temperature function used in BTS, $\alphabts(x)>0$. The temperature at a decision node $s$ is $\alphabts(N(s))$.
    \item[$\epsbts$]
        An exploration parameter used in BTS, $\epsbts\in[0,\infty)$.
    \item[$\Nqbts, \Nvbts$]
        \hspace{0.25cm} Pseudo-visit weights used in BTS to bias the Q-value and value estimates towards the heuristic functions $\Qinit$ and $\Vinit$.
    \item[$\pibts$]
        The search policy used in BTS.
    \item[$\Qbts(s,a)$]
        The Bellman Q-value estimate at chance node $(s,a)$ in BTS.
    \item[$\Qbtsnorm(s,a)$]
        The optionally normalised and heuristic-biased Q-value estimate used by the BTS search policy to select actions.
    \item[$\Vbts(s)$]
        The Bellman value estimate at decision node $s$ in BTS.
    \item[$\psibts$]
        The Q-value based recommendation policy of BTS: $\psibts(s)=\argmax_{a\in\cl{A}}\Qbts(s,a)$.
    \item[$\mvbts$]
        The most-visited recommendation policy of BTS: $\mvbts(s)=\argmax_{a\in\cl{A}} N(s,a)$.
    \\
    %%%%%
    % DENTS
    %%%%%
    \item[{\parbox[t]{\textwidth}{
        \Large\textbf{Decaying ENtropy Tree Search (Section \ref{sec:4-2-2-dents})}\hfill\hfill
    }}]
    \item[$\alphadents$]
        The temperature function used in DENTS, $\alphadents(x)>0$.
    \item[$\betadents$]
        The entropy weighting function used in DENTS, $\betadents(x)\geq 0$. Typically chosen such that $\betadents(x)\rightarrow 0$.
    \item[$\epsdents$]
        An exploration parameter used in DENTS, $\epsdents\in[0,\infty)$.
    \item[$\HQdents(s,a)$]
        The Monte Carlo entropy estimate at chance node $(s,a)$ in DENTS.
    \item[$\HVdents(s)$]
        The Monte Carlo entropy estimate at decision node $s$ in DENTS.
    \item[$\mvdents$]
        The most-visited recommendation policy of DENTS.
    \item[$\Nqdents, \Nvdents$]
        \hspace{0.25cm} Pseudo-visit weights used in DENTS, analogous to $\Nqbts$ and $\Nvbts$.
    \item[$\pidents$]
        The search policy used in DENTS.
    \item[$\psidents$]
        The Q-value based recommendation policy of DENTS.
    \item[$\Qdents(s,a)$]
        The Bellman Q-value estimate at chance node $(s,a)$ in DENTS.
    \item[$\Qdentssoft(s,a)$]
        The entropy-augmented Q-value used in the DENTS search policy: $\Qdentssoft(s,a)=\Qdents(s,a)+\betadents(N(s))\HQdents(s,a)$.
    \item[$\Qdentsnorm(s,a)$]
        The optionally normalised and heuristic-biased soft Q-value used by the DENTS search policy to select actions.
    \item[$\Vdents(s)$]
        The Bellman value estimate at decision node $s$ in DENTS.
    \\
    %%%%%
    % Ch 5 - CHMCTS
    %%%%%
    \item[{\parbox[t]{\textwidth}{
        \Large\textbf{Convex Hull Monte Carlo Tree Search \\(Chapter \ref{ch:5-chmcts})}\hfill\hfill
        }}]
    \item[$\alphachbts$]
        The temperature function used in CH-BTS.
    \item[$\bczt$]
        The bias parameter used in CZT to control exploration.
    \item[$\bpareto$]
        The bias parameter used in P-CHMCTS to control exploration.
    \item[$\cchuct$]
        The bias parameter used in CH-UCT to control exploration.
    \item[$\ctxreg(s,\pi^{1:n})$]
        The \textnormal{contextual cumulative regret} of the sequence of search policies $\pi^{1:n}$ at state $s$ over $n$ trials, where a weight vector is sampled uniformly from $\Delta^D$ at each trial.
    \item[$\ctxsreg(s,\psi)$]
        \hspace{0.45cm} The \textnormal{contextual simple regret} of a recommendation policy $\psi$ at state $s$: the expected scalarised loss relative to the optimal policy, with the weight vector drawn uniformly from $\Delta^D$.
    \item[$\deltaunsolved$]
        The confidence parameter used in the solved labelling of CHMCTS.
    \item[$\DST(W,\pswept)$]
        The \textit{Deep Sea Treasure} environment with width $W$ and probability of being swept $\pswept$ used in Chapter \ref{ch:5-chmcts}.
    \item[$\epschbts$]
        An exploration parameter used in CH-BTS.
    \item[$K_{\max}$]
        The maximum size of a convex hull value set in CHMCTS, used in the size pruning optimisation.
    \item[$\Mmin$]
        The minimum ball visit count required to trigger the CZT activation rule.
    \item[$\pi(a|s;\bff{w})$]
        A \textnormal{contextual policy}, extending the policy notation $\pi(a|s)$ to include a context weight $\bff{w}\in\Delta^D$.
    \item[$\pswept$]
        The probability of the agent being swept by a current in the \textit{Deep Sea Treasure} environment used in Chapter \ref{ch:5-chmcts}.
    \item[$\rref$]
        The reference point used in the hypervolume indicator (H-CHMCTS).
    \item[$\ruto$]
        The utopian point used in the Chebyshev utility (C-CHMCTS).
    \item[$\unsolvedtol$]
        The tolerance used to mark chance nodes as solved in CHMCTS, where a node is marked solved when $\unsolved(s,a)\leq\unsolvedtol$.
    \\
    %%%%%
    % CHMCTS Common Framework
    %%%%%
    \item[{\parbox[t]{\textwidth}{
        \Large\textbf{CHMCTS Common Framework (Section \ref{sec:5-3-1-framework})}\hfill\hfill
    }}]
    \item[$\Valg(s)$]
        The convex hull value set estimate maintained at decision node $s$ by a CHMCTS algorithm $\alg$.
    \item[$\Qalg(s,a)$]
        The convex hull Q-value set estimate maintained at chance node $(s,a)$ by a CHMCTS algorithm $\alg$.
    \item[$\Valgctx{\bff{w}}(s)$]
        The \textnormal{contextual value estimate} at decision node $s$ under weight $\bff{w}$: $\Valgctx{\bff{w}}(s)=\max_{\bff{v}\in\Valg(s)}\bff{w}^\top\bff{v}$.
    \item[$\Qalgctx{\bff{w}}(s,a)$]
        The \textnormal{contextual Q-value estimate} at chance node $(s,a)$ under weight $\bff{w}$: $\Qalgctx{\bff{w}}(s,a)=\max_{\bff{q}\in\Qalg(s,a)}\bff{w}^\top\bff{q}$.
    \item[$\pialg(a|s;\bff{w})$]
        The search policy of a CHMCTS algorithm $\alg$.
    \item[$\psialg(s;\bff{w})$]
        The recommendation policy of a CHMCTS algorithm $\alg$: $\psialg(s;\bff{w})=\argmax_{a\in\cl{A}}\Qalgctx{\bff{w}}(s,a)$.
    \\
    %%%%%
    % Ch 6 - Simplex Maps
    %%%%%
    \item[{\parbox[t]{\textwidth}{
        \Large\textbf{Simplex Maps for Multi-Objective Monte Carlo Tree Search \\(Chapter \ref{ch:6-simplexmaps})}\hfill\hfill
        }}]
    \item[$\ESM$]
        The set of undirected edges of a simplex map, $\ESM\subseteq\VSM\times\VSM$.
    \item[$\fSM$]
        The function mapping the vertices of a simplex map to value estimates.
    \item[$\fcv(\GSM,\bff{w})$]
        \hspace{2.55cm} Returns the (approximately) closest vertex in $\VSM$ to the weight vector $\bff{w}\in\Delta^D$.
    \item[$\fcs(\GSM,\bff{w})$]
        \hspace{3.45cm} Returns the leaf simplex in $\TSM$ that contains the weight vector $\bff{w}\in\Delta^D$.
    \item[$\GSM$]
        A simplex map, $\GSM=(\VSM,\ESM,\TSM,\fSM)$.
    \item[$\push(\GSM,\wSM)$]
        Propagates the value estimate at $\wSM$ to neighbouring vertices via breadth-first search.
    \item[$\pushradius$]
        The maximum push radius used by the $\push$ operation.
    \item[$\splitminradius$]
        \hspace{0.75cm} The minimum radius below which a simplex is not split.
    \item[$\splitmindelta$]
        \hspace{0.5cm} The minimum value-estimate difference within a simplex required to trigger a split.
    \item[$\splitminvis$]
        \hspace{0.6cm} The minimum number of split calls on a simplex before it is split.
    \item[$\splitsimplex(\GSM,\SSM)$]
        \hspace{1.2cm} Performs a longest edge bisection of the leaf simplex $\SSM\in\TSM$ when split conditions are met.
    \item[$\TSM$]
        The binary tree of simplices of a simplex map, whose leaf nodes form a triangulation of the unit simplex $\Delta^D$.
    \item[$\VSM$]
        The set of vertices of a simplex map, $\VSM\subseteq\Delta^D$.
    \item[$\wSM$]
        A vertex of a simplex map, $\wSM\in\VSM$.
    \\
    %%%%%
    % SM-DENTS
    %%%%%
    \item[{\parbox[t]{\textwidth}{
        \Large\textbf{DENTS with Simplex Maps (Section \ref{sec:6-3-algorithms})}\hfill\hfill
    }}]
    \item[$\alphasmd$]
        The temperature function used in SM-DENTS.
    \item[$\betasmd$]
        The entropy weighting function used in SM-DENTS.
    \item[$\epssmd$]
        An exploration parameter used in SM-DENTS.
    \item[$\Vsmd(s;\cdot)$]
        The multi-objective value estimate function maintained in the simplex map at decision node $s$.
    \item[$\Qsmd(s,a;\cdot)$]
        The multi-objective Q-value estimate function maintained in the simplex map at chance node $(s,a)$.
    \item[$\HVsmd(s;\cdot)$]
        The entropy value estimate function maintained in the simplex map at decision node $s$.
    \item[$\HQsmd(s,a;\cdot)$]
        The entropy value estimate function maintained in the simplex map at chance node $(s,a)$.
    \item[$\Vsmdctx(s)$]
        The contextual value estimate of SM-DENTS at decision node $s$: $\Vsmdctx(s)=\bff{w}^\top\Vsmd(s;\wV)$ where $\wV=\fcv(\GSM(s),\bff{w})$.
    \item[$\Qsmdctx(s,a)$]
        The contextual Q-value estimate of SM-DENTS at chance node $(s,a)$.
    \item[$\pismd$]
        The search policy used in SM-DENTS.
    \item[$\psismd$]
        The recommendation policy used in SM-DENTS: $\psismd(s;\bff{w})=\argmax_{a\in\cl{A}}\Qsmdctx(s,a)$.

\end{mclistof} 