% \begin{savequote}[8cm]
% \textlatin{Neque porro quisquam est qui dolorem ipsum quia dolor sit amet, consectetur, adipisci velit...}

% There is no one who loves pain itself, who seeks after it and wants to have it, simply because it is pain...
%   \qauthor{--- Cicero's \textit{de Finibus Bonorum et Malorum}}
% \end{savequote}

\chapter{\label{ch:1-intro}Introduction} 

    \minitoc

    \todo{chapter structure (i.e. in the introduction section I give some background in the field(s), cover the main 
    contributions of this thesis, etc, etc).}

\section{Overview}
\label{sec:1-1-overview}

    \todo{list}
    \begin{itemize}
        \item Give some context around MCTS (and talk about exploration and exploitation), and why we might use it
        \begin{itemize}
            \item Larger scale than tabular methods
            \item Can do probability and theory stuff (and some explainability, by looking at stats in the tree the agent used)
            \item Can use tree search with neural networks to get some of the above (and use for neural network training as in alpha zero)
        \end{itemize}
        \item Argument from DENTS paper for exploration > exploitation (in context of planning in a simulator)
        \item Give high level overview of Multi-Objective RL, and why it can be useful
        \item Give an idea of how my work fits into MCTS and MORL as a whole
        \item Discuss research questions/issues with current literature (i.e. introduce some of the ideas from contributions section below)
    \end{itemize}

\section{Contributions}
\label{sec:1-2-contributions}

    \todo{I'm not too happy with this section, I think most of the questions could be phrased better, but nothing I'm 
    writing sounds quite right to me at the moment. I also just tried to come up with as many questions as I could with 
    the idea of I don't need to keep them all}

    \todo{Also inline acronyms used, }

    Throughout this thesis, we will consider the following questions related to Monte Carlo Tree Search and Multi-Objective Reinforcement Learning:
    \begin{enumerate}[start=1, label={\textbf{Q\arabic* -}}]
        \item \hypertarget{q1}{\textbf{Exploration:}} When planning in a simulator, how can an algorithm best exploit the time it is given to produce the best recommendation action?
        \item \hypertarget{q2}{\textbf{Entropy:}} Entropy is often used as an exploration objective in RL, but can it be used soundly in MCTS?
        \item \hypertarget{q3}{\textbf{Complexity:}} MCTS algorithms typically run in $O(nAH)$, but are there algorithms that can improve upon this?
        \item \hypertarget{q4}{\textbf{Scalability:}} How can the scalability (with respect to size of environments) of multi-objective MCTS methods be improved?
        \item \hypertarget{q5}{\textbf{Curse of Dimensionality:}} To what extent do Multi-Objective MCTS methods suffer from the curse of dimensionality? (basically Multi-Objective complexity)
        \item \hypertarget{q6}{\textbf{Tree Evaluation:}} How can we best evaluate a search tree produced by a Monte Carlo Tree Search algorithm? \todo{add a matching contrib}
        \item \hypertarget{q7}{\textbf{Multi-Objective Evaluation:}} Can we apply methods from the MORL literature to theoretically and empirically evaluate Multi-Objective MCTS?
    \end{enumerate}

    \todo{some words about how below is the contributions we're making in this thesis and expand these bullets a bit more}
    \begin{itemize}
        \item Max Entropy can be misaligned with reward maximisation (\entropyq)
        \item Boltzmann Search Policies - BTS and DENTS (\exploreq, \entropyq, and eval \evalq)
        \item Use the alias method to make faster algorithms (\complexityq)
        \item Simple regret (\exploreq)
        \item Contextual regret introduced in CHMCTS (\scalabilityq, \morlevalq)
        \item Contextual Zooming and CHMCTS (runtimes cover \dimq, results \evalq)
        \item Simplex maps (\scalabilityq, \dimq)
        \item Contextual Simple Regret (\evalq, \morlevalq)
    \end{itemize}

    \hide{\todo{Would like to do the comparing different types of eval, even if not listing it as a research question 
    (compare giving it X seconds per decision and evaluating that policy (SLOW), and comparing policy extracted from 
    the tree)}}

    \hide{\todo{can make an argument that the best bound achieved by theory is given by letting temperature go to max. Which is consistent with the exploring bandits results}}



\section{Structure of Thesis}
\label{sec:1-3-thesis-structure}

    \todo{a paragraph with a couple lines to a paragraph about each chapter. This is the high level overview/intro to 
    the thesis paragraph. I.e. this section is ``this is the story of my thesis in a page or two''}

\section{Publications}
\label{sec:1-4-publications}

    \todo{update final publication when submit}

    The work covered in this thesis also appears in the following publications:
    \begin{itemize}
        \item Painter, M; Lacerda, B; and Hawes, N. ``Convex Hull Monte-Carlo Tree-Search." In \textit{Proceedings of the international conference on automated planning and scheduling. Vol. 30. 2020}, ICAPS, 2020, (see Appendix~\ref{app:p1-chmcts}).
        \item Painter, M; Baioumy, M; Hawes, N; and Lacerda, B.  ``Monte Carlo Tree Search With Boltzmann Exploration." In \textit{Advances in Neural Information Processing Systems, 36, 2023}, NeurIPS, 2023, (see Appendix~\ref{app:p2-dents}).
        \item Painter, M; Hawes, N; and Lacerda, B. ``Simplex Maps for Multi-Objective Monte Carlo Tree Search." In \textit{TODO}, \textbf{Under Review at conf\_name}, (see Appendix~\ref{app:p3-simplexmaps}).
    \end{itemize}