



\chapter{\label{ch:3-relatedwork}Related Work}

    \minitoc

    This chapter discusses related work on bandits, maximum entropy reinforcement learning, Monte-Carlo Tree Search, and multi-objective sequential decision making. The discussion is brief, and points to the most relevant references rather than giving a full treatment, as background material has already been covered in Chapter \ref{ch:2-background}. Where applicable, references are flagged for use in later chapters.




\section{Multi-Armed Bandits}
\label{sec:3-1-mab}

    Multi-armed bandits (MABs) and their variants are used for action selection throughout this thesis. This section only covers bandit results that are directly relevant to, or used in, later chapters.

    \paragraph{Best-arm identification and sequential halving.}
    While UCB targets cumulative regret, several MCTS variants in Section \ref{sec:3-3-mcts} target simple regret instead. In $K$-armed bandits, simple regret measures the suboptimality of a single recommended arm, rather than the total reward earned during exploration rounds. The most influential simple regret algorithm is the Sequential Halving procedure of \cite{seq_halving}. Given a fixed budget of arm pulls, Sequential Halving runs in $\lceil \log_2 K \rceil$ phases, samples the surviving arms uniformly within each phase, and discards the worse half at the end of each phase. The probability of returning the wrong arm decays exponentially in the budget, and the algorithm requires no parameters to be tuned. 

    \paragraph{Contextual bandits.}
    Contextual bandits extend the standard MAB by giving the agent a context on each round, which can be used when selecting an arm. The contextual zooming algorithm of \cite{cz}, later refined in \cite{cz_long}, assumes a similarity metric on the joint context-arm space, and exploits this structure to obtain regret bounds that adapt to the local geometry of the problem. \citet{linucb} take a different approach, and introduce LinUCB which assumes that the expected reward of each arm is a linear function of the context. The algorithm learns an estimate of the assumed linear function and uses a UCB-style confidence bound for exploration.

    \paragraph{Continuous-armed bandits.}
    For bandits with a continuous set of arms, the Hierarchical Optimistic Optimisation (HOO) algorithm of \cite{hoo,hoo_journal} maintains a tree-structured covering of the arm space, and assigns optimistic upper-confidence values to nodes. The partitioning is refined around regions of high reward to close in on a region containing the optimal arm. %Under a local Lipschitz assumption on the mean payoff function, HOO attains regret that is essentially independent of the dimension of the arm space.

    \paragraph{Multi-objective bandits.}
    \cite{pareto_ucb} generalise UCB to vector-valued rewards by applying an upper confidence bound across all dimensions of the reward vector, and selecting uniformly at random from the perturbed Pareto front. This algorithm, called Pareto-UCB, is shown to attain logarithmic \textit{Pareto regret}. \cite{pareto_ucb_2} provide an empirical follow-up that compares several variants on multi-objective Bernoulli benchmarks. Pareto-UCB is used by \citet{pareto_momcts} in an MOMCTS algorithm, and is used in Chapter \ref{ch:5-chmcts} as a baseline search policy.




\section{Maximum Entropy Reinforcement Learning}
\label{sec:3-2-rl}

    Maximum entropy reinforcement learning adds an entropy bonus on the policy to the standard expected return objective (Equation \ref{eq:2:soft_rl_obj_fn_def}). Earlier uses of entropy regularisation in sequential decision making include maximum-entropy inverse reinforcement learning \cite{max_ent_irl,max_ent_irl_thesis}, and policy gradient methods that include an entropy regularisation for exploration and to avoid policies degenerating to deterministic ones \cite{reinforce_ment,a3c,ppo}.

    In deep reinforcement learning, \citet{deep_energy_policies} apply the maximum entropy objective to value-based deep learning methods. %, and derive an energy-based policy by combining soft Q-learning with amortised inference. 
    \citet{sac} subsequently introduce Soft Actor-Critic (SAC), an off-policy actor-critic algorithm that has become a standard baseline for continuous control. SAC also introduces an automatic temperature-tuning rule, to help address the sensitivity of maximum entropy methods to the choice of $\alpha$. %The translation of these ideas from policy optimisation to tree search is the basis for the MENTS family of algorithms in the next section, and motivates the convergence analysis in Chapter \ref{ch:4-boltzmann}.

    \citet{tsallis_rl} replace the use of Shannon entropy with Tsallis entropy in the maximum entropy objective, and derive that optimal policies in this objective correspond to a \textit{sparsemax} distribution. The \textit{sparsemax} distribution is also a stochastic approximation to the max function, like the softmax, but it is less uniform in the output probabilities.








\section{Monte-Carlo Tree Search}
\label{sec:3-3-mcts}

    A broad survey of Monte-Carlo Tree Search prior to the deep learning era is given by \cite{mcts_survey}, which catalogues UCT variants, enhancements such as rapid action value estimate and progressive widening, and applications across games and planning. \cite{thts} introduce the Trial-Based Heuristic Tree Search (THTS) framework, which unifies a number of online MDP planning algorithms (including UCT) into a single template (covered in Section \ref{sec:2-4-2-thts}). THTS is also the framework in which several variants of UCT are first formalised. In particular, MaxUCT replaces the empirical-mean backups of UCT with full Bellman backups that take a maximum over child values. Closely related, but predating MCTS, is Real-Time Dynamic Programming \cite{rtdp} and its labelled variant LRTDP \cite{lrtdp}, which interleave Bellman backups with trial-based exploration of the state space.

    \paragraph{Simple-regret MCTS.}
    Several MCTS variants replace UCB with action-selection rules that target simple regret, with corresponding theoretical guarantees on the quality of the recommended action at the root node. Sequential Halving applied to Trees (SHOT) \cite{shot} applies the Sequential Halving procedure of \cite{seq_halving} recursively at every level of the tree. Hybrid MCTS (H-MCTS) \cite{hmcts} instead applies Sequential Halving only at the root, and uses UCT at internal nodes. The motivation is that simple regret guarantees are most needed at the the root node. BRUE \cite{brue} (Best Recommendation with Uniform Exploration) achieves an exponential simple regret bound by alternating between uniform action selection for exploration, and greedy action selection for value estimation. Each trial has an associated \textit{switching point}, where uniform exploration ends and greedy value estimation begins. %An earlier proposal in this direction is given by \cite{tolpin2012mcts}.

    \paragraph{Maximum-entropy MCTS.}
    \cite{ments} introduce Maximum ENtropy Tree Search (MENTS), which uses the soft Bellman backup and Boltzmann action selection of maximum entropy RL in MCTS (Section \ref{sec:2-4-4-ments}). MENTS is the basis for the Boltzmann tree search algorithms developed in Chapter \ref{ch:4-dents}. \cite{rentsmytents} subsequently generalise MENTS by replacing the Shannon entropy regulariser other entropy regularisers. RENTS is derived by using relative entropy (KL divergence) regulariser. TENTS is derived by using a Tsallis entropy regulariser similar to \cite{tsallis_rl}, and results in a sparsemax search policy.




\section{Multi-Objective Optimisation and Reinforcement Learning}
\label{sec:3-4-morl}

    \paragraph{Multi-objective optimisation.}
    Multi-objective optimisation is concerned with computing the Pareto front of a vector-valued objective. \citet{moo_chebyshev} reduces the problem to minimising the maximum weighted deviation from a utopian reference point, often referred to as the \textit{Chebyshev scalarisation} or utility. Varying the weight vector traces out the entire Pareto front, including its non-convex regions. In the evolutionary setting, NSGA-II \cite{nsga_ii} is a fast genetic algorithm that combines non-dominated sorting with a crowding distance heuristic to maintain diversity along the front. The crowding distance estimator is used in Chapter \ref{ch:5-chmcts} to prune points from convex hull value sets. In the multi-agent setting, \citet{cccs} introduce algorithms for computing the convex coverage set (CCS) of a multi-objective coordination graph. These include a variable-elimination procedure and an outer-loop linear-support method. The linear program used to prune dominated value vectors when the utility is linear is reused in this thesis \quest{ref to where used}.

    \paragraph{Optimisation criteria.}
    In Section \ref{sec:2-6-morl} the utility function is applied after taking the expectation of the return, which is referred to as the \textit{scalarised expected returns} (SER) criterion. \citet{survey_mo_seq_dec_make} explain that this is appropriate when the agent is evaluated over many independent executions of the policy, and when the agent is evaluated on a single execution it is more appropriate to use the \textit{expected scalarised returns} (ESR): $\max_\pi u(\mathbb{E}_\pi[\bff{G}])$, where $\bff{G}$ is the return of the policy. The two criteria coincide when $u$ is linear, which is the setting considered in this thesis, but in general the two criteria yield different optimal policies.  The majority of MORL algorithms in the literature target the SER criterion.

    \paragraph{Planning algorithms.}
    Planning approaches to MOMDPs predate the reinforcement learning literature. \citet{white_momdp} adapts dynamic programming to find Pareto-optimal policies for infinite-horizon discounted MOMDPs, but the resulting policies are non-stationary. \citet{con_modp} subsequently address this with the CON-MODP algorithm, which uses a consistency operator to enforce stationarity. Convex Hull Value Iteration \cite{chvi} extends Bellman's value iteration by storing a convex hull value set at each state-action pair. CHVI is covered in more detail in Section \ref{sec:2-6-1-chvi}. \citet{lizotte_spline_2d,lizotte_spline_nd} extend this approach by representing the value function in weight space rather than reward space, which gives piecewise-linear representations that scale more favourably with the number of states. The three-objective treatment of \citet{lizotte_spline_nd} relies on triangulation primitives from computational geometry, and the approach has been demonstrated mainly in two and three objectives.

    \paragraph{Inner-loop methods.}
    Inner-loop methods, which notably include Multi-Objective MCTS methods (Section \ref{sec:3-5-momcts}), modify the underlying solver to operate directly on vector-valued (or set-valued) value functions, and compute the entire coverage set in a single pass. \citet{locally_optimal} propose Pareto Q-learning, which is a model-free inner-loop method that maintains, for each state-action pair, a set of non-dominated value vectors, with dominated entries pruned after each update. \citet{mofqi} extend Fitted Q-Iteration to the multi-objective case by augmenting the state with the linear scalarisation weights, so that a single training run learns a Q-function parameterised by the weight vector. \citet{morl_chebyshev} apply the Chebyshev scalarisation of \citet{moo_chebyshev} to multi-objective Q-learning, which allows compromise solutions to be recovered under non-linear preferences.

    \paragraph{Outer-loop methods.}
    Outer-loop methods reduce the multi-objective problem to a sequence of single-objective problems, each obtained by fixing a scalarisation. The coverage set is then assembled from the single-objective solutions. The simplest version repeats a single-policy solver on a grid of weight vectors, but adaptive search procedures can identify the relevant weight vectors much more efficiently. Optimistic Linear Support \cite{cccs} is the most widely used outer-loop framework: it iteratively selects the weight vector that maximises an optimistic upper bound on the value of the current CCS approximation, and adds the corresponding scalarised solution to the set. Outer-loop methods are also common in the (multi-objective) formal verification literature, where \cite{prism_pareto} approximate the Pareto curve of a multi-objective probabilistic model-checking problem by repeatedly calling a single-objective value-iteration solver, as implemented in the PRISM model checker.

    \paragraph{Single-policy methods.}
    When the utility function and weight vector are fully known a priori, only a single policy needs to be returned. The simplest approach is to apply a scalarisation to the reward vector and solve the resulting single-objective MDP with a standard algorithm such as Q-learning. This is sound when the utility is linear, but for non-linear utilities the additivity of returns is broken, and the Bellman equation no longer holds \cite{survey_mo_seq_dec_make}. For the ESR criterion, \citet{eupg} introduce the Expected Utility Policy Gradient, which uses Monte Carlo rollouts to estimate the utility of full-episode returns. Distributional MCTS \cite{dmcts,dmcts_long}, discussed in Section \ref{sec:3-5-momcts}, also targets ESR.

    \paragraph{Deep MORL.}
    Deep multi-objective reinforcement learning extends the algorithms above to high-dimensional state and action spaces using neural function approximators. \citet{mossalam_modrl} combine the Optimistic Linear Support framework of \cite{cccs} with deep Q-networks, and compute the CCS by solving a sequence of scalarised MDPs. \citet{abels_dynamic_weights} consider the setting where user preferences change at execution time, and propose a single-DQN architecture that conditions the value estimate on the current weight vector, together with a diverse experience replay buffer that stores transitions across weight vectors. \cite{xu_prediction_guided} combine a multi-objective extension of PPO with an evolutionary algorithm to construct a continuous approximation of the Pareto front for continuous-control tasks. 




\section{Multi-Objective Monte-Carlo Tree Search}
\label{sec:3-5-momcts}

    \citet{og_momcts} present the first extension of MCTS to Multi-Objective MCTS (MOMCTS). A global \textit{Pareto archive} is maintained, with each tree node storing a point estimate of the vector-valued return. Action selection consists of perturbing value estimates at each node by a UCB-style confidence bound and selecting the perturbed point that leads to the largest hypervolume when combined with the Pareto archive. \cite{hv_momcts_1,hv_momcts_2,hv_momcts_3} develop and refine hypervolume-based MOMCTS by instead storing a Pareto front at each node, and using the hypervolume indicator directly in a UCB-style search policy.

    Two natural alternatives to the hypervolume indicator have been investigated. \cite{pareto_momcts} apply the Pareto-UCB rule of \cite{pareto_ucb} as a tree action-selection rule, which performs search directly on Pareto-dominance comparisons rather than on a scalar indicator. \cite{chebyshev_momcts} instead use the Chebyshev scalarisation of \cite{moo_chebyshev} as the basis for both node expansion and final move selection in MCTS. The motivation is that the Tchebycheff function, unlike linear scalarisation, can recover Pareto-optimal solutions in non-convex regions of the front.

    All of the above MOMCTS algorithms target the SER criterion. \cite{dmcts,dmcts_long} instead address the ESR criterion, and propose Distributional MCTS. At each chance node, Distributional MCTS maintains an approximate posterior distribution over the utility of the returns rather than an expectation, and uses Thompson sampling for action selection. 









